
 \section{Relationship Rules}
\begin{enumerate}
  \item \sout{Neither party may kiss one another. Kissing is defined as the touching of lips. The touching of one set of lips to another
   body part is allowed unless it breaks another following rule.} Voided as of 27/3/13
  \item Touching between the parties is limited to hugs. A hug is defined as the wrapping of arms around one and other, and
   must occur once per meeting between Sam and Danielle.
   \\\textbf{\emph{Amendment}}
  \begin{enumerate}
    \item Samuel is permitted to touch Danielle in the breast area, and the buttocks region, while both parties are in private. 
  \end{enumerate}
  \item  No Item or Favour owed, may be used to force either Sam or Danielle into forfeiting or losing a Wager, or dare. 
  Hours of time may not be used to force a party into doing something they are currently unwilling to do. 
  \\ \textbf{\emph{Amendment}}
  \begin{enumerate}
    \item However a Dare may be used in conjunction with an item or favour, if it does not adversely affect the intent 
    of the reward, or the goal set within the dare.
    \item  If it does change the intent. A new Dare must be made, to be completed at another time
  \end{enumerate}
  \item If copulation in the shower is to occur it should be done early in the wash cycle as to minimise, the loss of hot water.
  \item Copulation in the bath should be discouraged as to minimise water spillage, but groping and touching should be encouraged.
  \item Copulation in the pool is to be expected, assuming cover of darkness but limited due to chlorine
  \item When a Challenge/Dare is complete it is Crossed out, but may be reintroduced with an amendment at a later date.
  \item On Tuesday and Thursday, should Danielle or Sam attempt to communicate with each other via any Online means, 
  An hour of time will be given to the other. This does not include, After Hours Ramblings,Questions relating to Work, 
  the need for Danielle or Sam to destress and thus needing the other, Or goodnights if they extend from Monday or Wednesday 
  into the early hours of Tuesday or Thursday.
  \item A minimum of an hour must be given to the other party that you will be coming over, if you expect their place to be tidy,
  otherwise you have no grounds to complain.
  \item 
\end{enumerate}
 




 

 

 