
 \section{Wagers}
 \subsection{Oral Challenge:}
 \begin{samepage}
Take a photo Every 30 seconds, One Person Must Retain Composure, while the other proceeds to give Oral to them, 
out of sight of the camera.\\
  \indent $\sim$ \hspace{5mm} Danielle: Sam must stay out of sight underneath Danielle's hoop dress, while pleasuring 
  her to the best of his abilities using all available utilities, while she must
  act as if there is no activity that is 'twixt at her nethers'.\\
 \indent  $\sim$ \hspace{5mm}Sam: Danielle must stay hidden underneath a desk or similar performing whatever ministrations using 
  whatever pleases her to pleasure him, while he attempts not to blow his cover.\\

 
  For each individual photograph in which either party is visibly pleasuring or being pleasured, will provide the other 
  with an hour of your time in which to use freely.
 \end{samepage}

 \subsection{Can't Touch This}
\begin{samepage}
   \indent $\sim$ Until the time of November 9th, neither party may under any circumstances kiss the other. Danielle is 
   unable to touch Sam in any way, directly or indirectly, which could be interpreted as sexual. Sam on the other hand is
    allowed to touch at both the breast and butt area, but may not progress further. \\
    \textit{ Violations of these orders will result in: } 
    \begin{itemize}
      \item The other party being allowed the same opportunity you stole.
      \item A greater than five hundred word porn story containing only both parties.
      \item In the future at a later specified time, the offender will have to follow the innocent,
      around the house naked until such time as the innocent says otherwise or company arrives.
      \item The offender will also have to cook a dinner meal, as well as hand cook a dessert to
       accompany the food.  
    \end{itemize}
\end{samepage}
 

\subsection{Who's' on first} 
\begin{samepage}
   \indent $\sim$ When the time comes that Sam and Danielle eventually copulate, the bed in which the coitus occurred, 
   will be deemed loser, and the other will be given 5 Hours to use at their discretion to have coitus in the losers bed.
\end{samepage}
 

 \subsection{A Song of Desire and Entice (Game of moans)}
\begin{samepage}
   \indent $\sim$ During the viewing of HBO's Game of Thrones, at every sex scene at the end of the scene,
    the show will be paused, and both parties will attempt to bring the other to orgasm.  
    The show will resume when either party has orgasmed. The loser is the first person to desire not to copulate
     but instead return to viewing the show. At that time the winner will receive the amount of hours equaling the total 
     number of episodes watched.

 

 \subsection{Riding on empty} 

   \indent $\sim$ On a day agreed to by both parties, Danielle will attempt to copulate with Sam until  
     such a point that Sam is no longer able to produce an orgasm, or Danielle backs out.  
     The loser will have to give a full body massage to the victor to rub away the pain of 
     coitus. 
\end{samepage}
 

 \subsection{Sex-ting in plain sight}  
\begin{samepage}
  \indent $\sim$ As in rule B99.2 after an hour of nothing but socializing in a group, both parties must  
     sext one and other, assuming the technology is available to do so. Both parties must attempt to hide the fact from the group, 
     that Danielle and Sam are sex-ting one and other. \\
     \indent $\sim$ \hspace{5mm} If either party is caught sex-ting the other, then they are defined as the loser.
       Being caught is defined as being the person on the receiving end of a sext when it is  
       brought to the attention of the group or a subset of.\\ 
     \indent $\sim$ \hspace{5mm} The loser must suffer sensory deprived coitus. A blind fold and earplugs will be 
       employed, and the losing part must not make a noise or touch the winner at all in any way shape or form. 
\end{samepage}
\subsection{Ready Set Blow}
\begin{samepage}
\indent $\sim$ After the prescribed period in which copulation cannot occur, a day will be prescribed in which both 
	Danielle and Sam having not been pleasured for over 24 Hours will attempt this dare. \\
	In this dare both parties will race, predominately through the use of oral techniques to pleasure the other party. 
	This pleasure will occur in a sideways 69 Position, as to give no party leverage over the other \\
	\indent $\sim$ \hspace{5mm} This does not mean that oral techniques be the only techniques employed, but a majority stakehold
	in the pleasure caused.
	The winners is defined as the party who first caused a climax. The winner will recieve A complimentary Season worth of time,
	Along with the ability to recieve Oral pleasure in 5 Unique Locations, excluding the bedroom.
	The loser will recieve a Movies worth of time, along with being finished of the impending climax, for efforts applied
	
\end{samepage}
\begin{samepage}
\subsection{She can’t take much more, Colonel}
\indent $\sim$ Sam Sets out that irrespective of Wager E2, If Danielle is able to hold out past the date of 23/06/13
(3 months from setting) For every 7 Day period after that time, she will receive quarter season of time, for her strong will.\\
\indent $\sim$ \hspace{5mm}If Sam is unable to contain himself and breaks wager E2 before the allotted time, 
then this Wager will hold, meaning that While Sam may be able to kiss Danielle, if Danielle where to initiate a 
Kiss then this Wager is forfeit and she will no longer receive the payment of the wager.\\
If Danielle Kisses Sam at any point then this dare is forfeit and all debts will be payed.

\end{samepage}