
 

 \section{Dares}

 \renewcommand{\theenumi}{\thesubsection.\arabic{enumi}}

   \subsection{Danielle Dares Sam}

\begin{enumerate}
\item  To stay up and watch the sun to rise with her and kiss her the moment its above the horizon.

\item  To go 2 Hours without making an innuendo, and if he manages to achieve such a feat, will receive fellatio.

\item  To meet her at an establishment pretending not to know her, and attempt to pick her up.

\item  To have a physical Poke war. 

\item  To dress in fitting historical costuming (Toga, Bulla, etc.) and read to her a translation of her favourite poems.  Assuming she can hold out  jumping on him, special reward ensues - must be completed to find out.  hehe 

\item  To sleep with her in her car, preferably during heavy rain (insert `very wet' joke here) 
\end{enumerate}

 

  \subsection{Sam Dares Danielle:}

\begin{enumerate}
\item  To sleep with him with Dynamite by Taio Cruz, playing in background .

\item  To go 2 Hours without Making any reference to history, and if she manages such a feet of the calibre of the labours of Hercules, will receive Cunnilingus. 

\item  To spend all possible time in a day With no clothes on

\item  To awaken Samuel via means of Fellatio.

\item  To Skinny-dip along with Sam in her pool.

\item  To wear her skirt 3 inches above her knee for a single day.

\item  To Do activities in Her car with Sam so that the windows fog, to a point where it is impossible to see from the outside in or the inside out.

\item  To Kiss him in the rain.
\end{enumerate}
