\section{Miscellaneous Rules}

 \begin{enumerate}
   \item Do not talk about the //
   \item DO NOT talk about the //
   \item If you must talk about the //, it is the  `slash' and should be addressed as any other fanfiction we mutually read.
   \item When talking about the //, Pseudonyms will be used, no exceptions.
   \item When referring to a Rule You cannot call it a Rule. No exceptions.
   \item If you must refer to a Rule refer to it by Code “B06” No exceptions.
   \item If you wish to invoke an Owe While in the presence of another, make obscure reference only Or DON’T.
   \item McShep is the OTP. End of Story.
   \item All apples must be consumed by slicing into the apple with a knife, cutting it into pieces.
   \setcounter{enumi}{11}
   \item Anything you say can and will be used against you.
   \item Anything you do can and will be used against you, so you do it again.
   \setcounter{enumi}{33}
   \item If its going to be done, its on the list
   \item If its not on the list it will be added
   \setcounter{enumi}{98}
   \item Sam and Danielle agree that they are both open to degrees of sexual experimentation assuming 
   both parties are on board and does not impair physical, mental or emotional wellbeing. 
   \\ \textbf{\emph{Amendment}}
  \begin{enumerate}
    \item If an hour passes unable to decide what to do, the defaulted choice is sexual experimentation.
    \item  If an hour has passed with no decision being made, and Danielle and Sam are in a social outing 
    and unable to perform rule B99.1, the two must default to Sex-ting each other. 
  \end{enumerate}
 \end{enumerate}
 