

 

 \section{Owing}
 It is agreed upon that In regards to Hours that the equation
 \large
 \begin{align}
 \text{Hours} &= \frac{22(42\phi)+150\mu + 60\eta}{60}\\
 &= \frac{924}{60}\phi + \frac{150}{60}\mu + \frac{60}{60}\eta\\
 &= \frac{77}{5}\phi + \frac{5}{2}\mu + \eta\\\nonumber
  \text{where}\\ \nonumber
 \phi &=  \text{Number of Seasons Owed}\\\nonumber
 \mu &=  \text{Number of Movies Owed}\\\nonumber
 \eta &=  \text{Number of Extra Hours Owed}
 \end{align}
 
 

  
 \normalsize
 \subsection{Danielle}

 \begin{itemize}
   \item Danielle, has 5 Seasons and 1 Hour (77 Hours) of Sam's time to do with as she wishes.\\
    \begin{tabular}{r|rrr|l|r}
 		Date&Season&Movies&Extra&Change&Total\\
 		\hline
 		10/3/2013&+5&	&	&+77	&77\\
 		26/3/2013&	&	&+1	&+1		&78\\
 		\hline
 		\hline
 		Total&5&0&1&&78
 	\end{tabular}
   \item Free Pass To do as Danielle pleases.
   \item The Power to Dictate the clothing choice, for Sam, on any singular day
   \item The choice of 2 Fan Fictions in which Sam must himself read.
   \item The decision for which book, from which chapter, must Sam read aloud.
 \end{itemize} 
\newpage

 

   \subsection{Samuel}
   \begin{itemize}
     \item Samuel has 6 Seasons, 5 Movies and 4 Hour (109 Hours) of Danielle's time to do with as he wishes.\\
     \begin{tabular}{r|rrr|l||r}
 		Date&Season&Movies&Extra&Change&Total\\
 		\hline
 		10/03/2013&+5&+3	&		&+85	&85 \\
 		16/03/2013&+1&+2	&		&+21	&105\\
 		19/03/2013&	 &		&+1		&+1		&106\\
 		21/03/2013&	 &		&+1		&+1		&107\\
 		26/03/2013&	 &		&+2		&+2		&109\\
 		02/04/2013&	 &		&+1 	&+1		&110\\
 		04/04/2013&	 &		&+1		&+1		&111\\
 		\hline
 		\hline
 		Total&6&5&6&&111
 	\end{tabular}
     \item Sam has the duty to complete the task of combining sex and chocolate.
     \item An Hour of Danielle's time to do with it as he will, or else substitute it for cake.
     \item A free pass to do with her as his every desire commands
     \item The quest to acquire something Danielle can not give.
     \item The Power to Dictate the clothing choice, for Sam, on any singular day as Punishment against
     \item Sam may dictate at any single time in which Danielle must oblige and supply a full body massage.
     \item At a later date, Danielle must determine how she will ``Sell herself out for her research''.
     \item A Creative Mathematical Themed Idea to be determined.
     \item 5 Minutes of Brain Hug
     \item 
   \end{itemize}
    