
 \section{Situational Rules}

 \begin{enumerate}
   \item Should one party be given a ring of immense power that must be destroyed by completing a long journey, they agree to traverse the path together, 
   and kill any creepy half human things that attempt to help them, and carry the partner should they need it.
	\\ \textbf{\emph{Amendment}}
  	\begin{enumerate}
    	\item Simply call the flying Eagles
    	\item Do not hesitate to destroy ring in fires
    	\item Use Elvish as frequently as plot allows
  	\end{enumerate}
  	
   	\item Should either party find a Book in which if a name is written, that person should die, We will both work together 
   to become a seemless killing machine with ourselves placed as gods, and work together to play Xantatos Chess.
   \item If awaken to find ourself’s within confines of faerytale realm, Danielle gets to be the conquering Heroine who saves Sam from peril.
   \item Should either party decide that Meat is no longer required and thus turn vegan or vegetarian, the other party will proceed to slap 
   them with Cow and Pig or force feed them curry.
   \item When one party is studying/working/concentrating, the other party agrees to leave them alone and not attempt to seduce them with sex.
   \\ \textbf{\emph{Amendment}}
  \begin{enumerate}
    \item Should the rule be broken, the other must give a full body massage to the Worker.
  \end{enumerate}
  \item Should Danielle Be captured by a Giant Mutant Turtle beast, And Sam goes on an adventure, surpassing many challenges, Danielle will 
  leave a note on the front of the Castle she is actually in, or scream as to give Sam an indication whether or not to fight his way through the castle.
  \item 
  \item If either party gains the Ability to fly or teleport through Super Powers, Magic, or otherwise, they agree to fly/teleport the other as both a means
   of travel, and as a joyful activity.
 \begin{samepage}
   \item Should Either party Gain a Super Powers, or magic via any means they will endeavour to empower the other with complementing or contrasting abilities 
   so as to form a Super Hero Team.
   \\ \textbf{\emph{Amendment}}
  \begin{enumerate}
    \item Costumes should be inventive, not derivative and not involve external underwear,spandex of any kind or leather pants.
    \item NO CAPES
    \item If Children are in the future, we shall ensure that the powers are genetic, or else given to them at an early age as to teach them to handle them.
   \end{enumerate} 
  \end{samepage}
  
  \item Should either of us discover a Fob watch, we gift it to the other person as to let them determine the calibre of TimeLord/Lady
  \\ \textbf{\emph{Amendment}}
  \begin{enumerate}
    \item If it is discerned that the timelord is malicious, we hunt for Tardis
    \item If Timelord is nice, then we agree to open, with promise of travelling universe together. 
  \end{enumerate}
  \item In the situation that a Condom cannot be found, then...
  \item Should Either become an Evil Genius or Overlord, they will follow the Evil Overlord list, 
  as they are logical and will help them enslave the populations. 
  \item If either acquires the technology to create nanobots to shape the universe for their own gain, 
  they agree that they will keep with the terms agreed upon originally discussed.
  \setcounter{enumi}{30}
  \item If either of us invents time travel we will ensure to make the Vehicle in a which we traverse time and space to either be an 
  infinitely large blue police box, or a Delorean.
  \\ \textbf{\emph{Amendment}}
  \begin{enumerate}
    \item Sex in either is fine, and encouraged.
  \end{enumerate}
  
  \item Should either party Become a Zombie, with an almost nil chance of a antivirus being developed Then Depending 
  on nature of Zombies:
   \\ \textbf{\emph{Amendment}}
  \begin{itemize}
    \item  For Intelligent zombies that posses brain capacity and are simply the undead with a craving for brain -
     we bite the other and gain immortality.
     \item For mindless meandering zombies - shoot first cry later, however the method of death must be enacted by 
     the non zombie party, assuming it is possible given circumstances.  
  \end{itemize}
  
  \item  In the event both Danielle and Sam switch bodies, They agree to teach the other everything they can about their mannerisms and persona, 
  as well as doing all things sexual to both themselves and their partner, and going out experiencing everything they can about the 
  other person’s life.  
  \item In the Event of a Gender Swap of both parties it is agreed that they will attempt to  progress along the linear progression of 
  ‘bases’ until such a point as awkwardness overcomes pleasure. They will also a session of Cosplaying assuming costumes fit, or the 
  genderswap lasts a time that costumes can be bought.
  \\ \textbf{\emph{Amendment}}
  \begin{enumerate}
    \item In the case of only Danielle being Gender swapped it is agreed that they will attend a Strip club together as gentlemen, 
    drink scotch while puffing cigars, and also attempt to conduct a Devil’s threeway. There will also be a session of mutual 
    masterbation along with an attempted 69.
    \item In the case of only Sam being Gender swapped we have a ‘girls day out’ and then get dressed up and go clubbing, afterwhich
     a session of Lesbian Sex, where Danielle performs cunninglingus on Sam.
  \end{enumerate}
  \item In a situation where one party is covered in whipped cream, or any other condiment of appeal, for the sensation
   of sexual pleasure, the other is duty bound to lick it all off.
  \item If health does not permit any form of contact between the pair, it is agreed that sex-ting via means of SMS messaging, 
  Skype voice/video or text chat or facebook text chat is to be employed until such time that the sick is nursed back to 
  health with care and affection. 
  \item Oral Pleasure while either Danielle or Sam are driving while may seem like a good idea on paper will never be put into practice
  \\ \textbf{\emph{Amendment}}
  \begin{enumerate}
    \item This does not mean that a simulated experience cannot occur, but this shall never occur while the vehicle is ``Turned on''. 
  \end{enumerate}
  
  \item In the event of accidental incident with time travel, it is agreed that Sam protects Danielle with the benefits of 
  masculinity, while Danielle attempts to understand period and use knowledge to benefit both. 
  \item If Sam or Danielle rise to the ranks in the underworld or heaven, assist their human to rise with the, assuring 
  them a decent place in underworld.
  \item Should One party make a deal with Satan thus leading the other on a Quest through the Inferno in an effort to save 
  the other from satan's grasp, it is agreed that the angelic party who has been taken by satan, will help through Divine 
  intervention wherever plot allows it, and will ensure a spot in the 1st Sphere of Paradiso.
  \item Should either party be taken by an incubi or succubi, it is agreed that this is not a form of cheating and both parties 
  will attempt to slay the foul creature and raise bastard half satanic children as their own.   
  \item In the event of parties being sucked into science fiction novel, both parties will proceed as quickly as possibly to acquire towels.
  \item We agree we will never be apart of the people that go to the special hell reserved for child molesters and people who talk in the cinema.
  \item In the case that someone learns about the //  we either employ blackmail or Physical force.
  \\ \textbf{\emph{Amendment}}
  \begin{enumerate}
    \item Physical force may include but is not limited to: 
    \begin{itemize}
      	\item  Murder
		\item  Stabbing
		\item  Retinas burnt out with Giant Laser
		\item  Frontal Lobe scooped out
		\item  Hands cut off
		\item  Crucifixion
		\item  light tapping on the shoulder
		\item  Chinese Water torture  
    \end{itemize}
  \end{enumerate}
  
  \item If either party is upgraded, then we agree to contain party and attempt to transplant brain.
  \item Should the ability to clone oneselves become commonly avaliable or developed by either party, then the Clones are restricted to a maximum of 5,
   and are welcome to be used as ‘sex toys’. 
   \item In the event of a crossover or transvergence with Parallel universe, we agree to meet alternate forms of self and determine from there 
   possibility of a threesome or greater. 
  \setcounter{enumi}{52}
  \item Should it be discovered that either Sam or Danielle are actually creatures inhabiting a body, 
  as per the conventions of a non-harmful symbiotic relationship, it is agreed that they will not judge the other or 
  attempt to enslave humans throughout the galaxy, or perpetuate hybrid race with their larva in navel cavity.
  \item Should either party have the genes of a long dead Hyper intelligent Race, we agree to take the other to the 
  long lost city, should we be invited to go on the expedition.
  \item Should either party ascend, particularly Danielle, it is agreed that the newly ascended will visit and attempt 
  to help the ascension process, but not before sharing themselves with the other.
  \item In the event that both of our families start a long feud, and we are caught in the middle of it, we agree we will 
  send messages before doing anything drastic.
  \setcounter{enumi}{68}
  \item If a situation arises such that both Sam and Danielle are wanting to please the other Orally and neither wishes 
  to wait then both shall perform the oral in the sexual position 69.
  \setcounter{enumi}{70}
  \item In any given disagreement, pausing and resuming are always an option, with no repercussions for doing so, as well 
  as requesting for a breather to gather thoughts and speak calmly.
  \item In the event of an altercation between Sam and Danielle, then they both agree that at the end of the fight, make up sex will ensue.
  \\ \textbf{\emph{Amendment}}
  \begin{enumerate}
    \item If the fight is about sex, this is probably a bad idea, and some other form of tension alleviating activity should be undertaken as to 
    reinforce the finality of the particular altercation
  \end{enumerate}
 \end{enumerate}
