
 \section{Situational Rules}

 \begin{enumerate}
   \item Should one party be given a ring of immense power that must be destroyed by completing a long journey, they agree to traverse the path together, 
   and kill any creepy half human things that attempt to help them, and carry the partner should they need it.
	\\ \textbf{\emph{Amendment}}
  	\begin{enumerate}
    	\item Simply call the flying Eagles
    	\item Do not hesitate to destroy ring in fires
    	\item Use Elvish as frequently as plot allows
  	\end{enumerate}
  	
   	\item Should either party find a Book in which if a name is written, that person should die, We will both work together 
   to become a seemless killing machine with ourselves placed as gods, and work together to play Xantatos Chess.
   \setcounter{enumi}{3}
   \item Should either party decide that Meat is no longer required and thus turn vegan or vegetarian, the other party will proceed to slap 
   them with Cow and Pig or force feed them curry.
   \item When one party is studying/working/concentrating, the other party agrees to leave them alone and not attempt to seduce them with sex.
   \\ \textbf{\emph{Amendment}}
  \begin{enumerate}
    \item Should the rule be broken, the other must give a full body massage to the Worker.
  \end{enumerate}
  
  \setcounter{enumi}{9}
  \item Should either of us discover a Fob watch, we gift it to the other person as to let them determine the calibre of TimeLord/Lady
  \\ \textbf{\emph{Amendment}}
  \begin{enumerate}
    \item If it is discerned that the timelord is malicious, we hunt for Tardis
    \item If Timelord is nice, then we agree to open, with promise of travelling universe together. 
  \end{enumerate}
  \item In the situation that a Condom cannot be found, then...
  \item Should Either become an Evil Genius or Overlord, they will follow the Evil Overlord list, 
  as they are logical and will help them enslave the populations. 
  \item If either acquires the technology to create nanobots to shape the universe for their own gain, 
  they agree that they will keep with the terms agreed upon originally discussed.
  \setcounter{enumi}{31}
  \item If either of us invents time travel we will ensure to make the Vehicle in a which we traverse time and space to either be an 
  infinitely large blue police box, or a Delorean.
  \\ \textbf{\emph{Amendment}}
  \begin{enumerate}
    \item Sex in either is fine, and encouraged.
  \end{enumerate}
  \setcounter{enumi}{34}
  \item Oral Pleasure while either Danielle or Sam are driving while may seem like a good idea on paper will never be put into practice
  \\ \textbf{\emph{Amendment}}
  \begin{enumerate}
    \item This does not mean that a simulated experience cannot occur, but this shall never occur while the vehicle is ``Turned on''. 
  \end{enumerate}
  \setcounter{enumi}{41}
  \item In the event of parties being sucked into science fiction novel, both parties will proceed as quickly as possibly to acquire towels.
  \item In the case that someone learns about the //  we either employ blackmail or Physical force.
  \\ \textbf{\emph{Amendment}}
  \begin{enumerate}
    \item Physical force may include but is not limited to: 
    \begin{itemize}
      	\item  Murder
		\item  Stabbing
		\item  Retinas burnt out with Giant Laser
		\item  Frontal Lobe scooped out
		\item  Hands cut off
		\item  Crucifixion
		\item  light tapping on the shoulder
		\item  Chinese Water torture  
    \end{itemize}
  \end{enumerate}
  \setcounter{enumi}{52}
  \item Should it be discovered that either Sam or Danielle are actually creatures inhabiting a body, 
  as per the conventions of a non-harmful symbiotic relationship, it is agreed that they will not judge the other or 
  attempt to enslave humans throughout the galaxy, or perpetuate hybrid race with their larva in navel cavity.
  \item Should either party have the genes of a long dead Hyper intelligent Race, we agree to take the other to the 
  long lost city, should we be invited to go on the expedition.
  \item Should either party ascend, particularly Danielle, it is agreed that the newly ascended will visit and attempt 
  to help the ascension process, but not before sharing themselves with the other.
  \item In the event that both of our families start a long feud, and we are caught in the middle of it, we agree we will 
  send messages before doing anything drastic.
  \setcounter{enumi}{68}
  \item If a situation arises such that both Sam and Danielle are wanting to please the other Orally and neither wishes 
  to wait then both shall perform the oral in the sexual position 69.
  \setcounter{enumi}{70}
  \item In any given disagreement, pausing and resuming are always an option, with no repercussions for doing so, as well 
  as requesting for a breather to gather thoughts and speak calmly.
  \item In the event of an altercation between Sam and Danielle, then they both agree that at the end of the fight, make up sex will ensue.
  \\ \textbf{\emph{Amendment}}
  \begin{enumerate}
    \item If the fight is about sex, this is probably a bad idea, and some other form of tension alleviating activity should be undertaken as to 
    reinforce the finality of the particular altercation
  \end{enumerate}
 \end{enumerate}
