
 

 \section{Dares}

 \renewcommand{\theenumi}{\thesubsection.\arabic{enumi}}

   \subsection{Danielle Dares Sam}

\begin{enumerate}
\item  To stay up and watch the sun to rise with her and kiss her the moment its above the horizon.

\item  To go $2$ Hours without making an innuendo, and if he manages to achieve such a feat, will receive fellatio.

\item  To meet her at an establishment pretending not to know her, and attempt to pick her up.

\item  To have a physical Poke war. 

\item  To dress in fitting historical costuming (Toga, Bulla, etc.) and read to her a translation of her favourite poems.  Assuming she can hold out  jumping on him, special reward ensues - must be completed to find out.  hehe 

\item  To sleep with her in her car, preferably during heavy rain (insert `very wet' joke here) 

\item To perform Cunnilingus, after consuming ananas Juice.

\item To To Allow her to lick Tabasco Sauce off of him.

\item To Allow her to lick wasabi off of him.

\item To Take her against a wall.

\item To Take her against a bookcase.

\item To watch a Tim burton Marathon.

\item To take her Doggy Style

\item To watch `A Dogs Breakfast' with her

\item To have a strip board games night

\item To watch SuperHeroes Movie Marathon

\item To sleep until no longer tired

\end{enumerate}

 

  \subsection{Sam Dares Danielle:}

\begin{enumerate}
\item  To sleep with him with Dynamite by Taio Cruz, playing in background .

\item  To go 2 Hours without Making any reference to history, and if she manages such a feet of the calibre of the labours of Hercules, will receive Cunnilingus. 

\item  To spend all possible time in a day With no clothes on

\item  To awaken Samuel via means of Fellatio.

\item  To Skinny-dip along with Sam in her pool.

\item  To wear her skirt 3 inches above her knee for a single day.

\item  To Do activities in Her car with Sam so that the windows fog, to a point where it is impossible to see from the outside in or the inside out.

\item  To Kiss him in the rain.

\item To attempt an underwater blowjob.

\item To ride him Cowgirl/Reverse Cowgirl.

\item Wash Her car in a bikini and White Tshirt.

\item Watch the Original Stargate Movie without saying a word. Reward 10 Seasons.

\item \sout{To play 50 In game days of COC with a Text Snapshot of character ever 5.} Completed 13/04/13

\item To perform Felatio while playing Video Game

\item Strip Video Games night

\item Write a Porn Roleplay Story together then act it out

\item To Allow Sam to Draw a Tattoo on Danielles Body in Marker and wear it for 24 Hours




\end{enumerate}
